GMSE: an R package for generalised management strategy evaluation

### 2017-07-17 notebook/ms/ms.Rmd
Minor change

---
title: 'GMSE: an R package for generalised management strategy evaluation'
author: A. Bradley Duthie, Jeremy J. Cusack, Roc&#0237;o Pozo, O. Sarobidy Rakotonarivo,
  and Nils Bunnefeld
date: '`r Sys.Date()`'
output:
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
  pdf_document:
    fig_caption: yes
  html_document: default
linestretch: 1
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
bibliography: gmse.bib
---

>>>>

---
title: 'GMSE: an R package for generalised management strategy evaluation'
author: A. Bradley Duthie, Jeremy J. Cusack, Roc&#0237;o Pozo, O. Sarobidy Rakotonarivo,
  and Nils Bunnefeld
date: '`r Sys.Date()`'
output:
  html_document: default
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
linestretch: 1
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
bibliography: gmse.bib
---
